---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# proteomicsHF

<!-- badges: start -->
[![GitHub license](https://img.shields.io/github/license/Naereen/StrapDown.js.svg)](https://github.com/pranavdorbala/proteomicsHF/blob/main/LICENSE)
[![ForTheBadge built-by-developers](http://ForTheBadge.com/images/badges/built-by-developers.svg)](https://github.com/pranavdorbala/proteomicsHF)
<!-- badges: end -->

proteomicsHF is a package with Functions necessary to analyze and replicate 
results of biomarker discovery pipeline for SOMALogic 5K Assay proteins 
associated with incident heart failure. Results are cached and derived from the 
Atherosclerosis Risk in Communities (ARIC) cohort from visits three and five. 
Includes functions to set adjustment variables, impute missing variables, 
summarize data, conduct uni-protein and multi-protein analyses and visualize 
data. Also includes a number of utility functions for data manipulation and 
reporting.

## Installation

Install the latest version of proteomicsHF from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pranavdorbala/proteomicsHF")
```
## Set Up

This is is how you set up multicore processing:

```{r example}
library(proteomicsHF)

set.seed(101010)

#Set number of cores according to system
doParallel::registerDoParallel(8) # 2 * system cores
future::plan(future::multisession, workers = 4) # number of system cores

```
